---
title: "`AssignmentCheck`: automatic check for your students"
author: "George Moroz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{`AssignmentCheck`: automatic check for your students}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## 1. Installation
Since `lingtypology` is an R package, you should install [R](https://www.r-project.org/) on your PC if you haven't already done so. To install the `lingtypology` package, run the following command at your R IDE, so you can also get the development version from GitHub:
```{r, eval= F}
install.packages("devtools")
devtools::install_github("agricolamz/AssignmentCheck")
```

Load package:
```{r}
library(AssignmentCheck)
```

## 2. Checks
Imagine that we have a directory with some files from your students
```{bash}
cd /home/agricolamz/_DATA/OneDrive1/_Work/github/markdown_check/tests
ls
```

As you can see, there are `.Rmd` files, and one `.txt` file. `test_files` function can take all `.Rmd` files and check, whether `R` code in `R` chunks produce the same result that we expected.

```{r}
setwd("/home/agricolamz/_DATA/OneDrive1/_Work/github/markdown_check/tests")
fit <- lm(mpg~cyl, mtcars)
test_files(expectations = list(4, fit$coefficients))
```

There is a variable `keyword_prefix` that defines the common part of the keywords, so you can ask your students to put their answer code chunks after some keywords. By default `keyword_prefix` is `"### "`, so your students can write "### 1.1", "### 1.2" and so on. But you can specify your own prefixes.

## 3. Citing `AssignmentCheck`
It is important to cite R and R packages when you use them. For this purpose use the `citation` function in R:
```{r}
citation("AssignmentCheck")
```
